Spatio-temporal estimates of risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa

### 2022-03-24 src/docs_amazon-poster/amazon-poster.Rmd
Update # of surveys

* We used 48 household surveys (AIS, BAIS, DHS, PHIA)
* For the categories $k \in \{1, 2, 3^{+}\}$ we used all the data to fit a survey-weighted multinomial logistic regression via the multinomial-Poisson transformation
\begin{align}
    &y_{itak}^\star \sim \text{xPoisson}(\kappa_{itak}), \\
    &\log(\kappa_{itak}) 
    = \underbrace{\theta_{ita}}_{\text{Observation (IID)}}
    + \underbrace{\beta_k}_{\text{Category (IID)}}
    + \underbrace{\alpha_{ak}}_{\text{Age (IID)}} \\
    &+ \underbrace{\zeta_{ck}}_{\text{Country (IID)}} 
    + \underbrace{\phi_{ik}}_{\text{Spatial (Besag)}} 
    + \underbrace{\gamma_{tk}}_{\text{Temporal (AR1)}}
\end{align}
where $p_{itak} = \text{softmax}(\kappa_{ita})_k$
* To differentiate $3^{+}$ we used the 13 surveys with a transactional sex question to fit a survey-weighted logistic regression
\begin{align}
    &y_{ia4}^\star \sim \text{xBinomial} \left( y_{ia3} + y_{ia4}, p_{ia4} / (p_{ia3} + p_{ia4}) \right), \\
    &\text{logit}(p_{ia4} / (p_{ia3} + p_{ia4}))
    = \beta_0
    + \beta_\texttt{cfswever} x_c \\
    &+ \underbrace{\alpha_a}_{\text{Age (IID)}}
    + \underbrace{\zeta_c}_{\text{Country (IID)}}
    + \underbrace{\phi_i}_{\text{Spatial (Besag)}}
\end{align}
where $x_c$ is the proportion of men in each country who are clients of FSW [@hodgins2021cfsw]
* We aligned our FSW estimates to the national-level UNAIDS Key Populations Atlas [@johnston2022deriving]
* Using the Poisson formulation facilitated inference using integrated nested Laplace approximation [@rue2009approximate] via `R-INLA`
* We estimated incidence and number of new infections by risk group using the risk ratios to disaggregate Naomi model [@eaton2021naomi] general population incidence estimates

>>>>

* We used 47 household surveys (AIS, BAIS, DHS, PHIA)
* For the categories $k \in \{1, 2, 3^{+}\}$ we used all the data to fit a survey-weighted multinomial logistic regression via the multinomial-Poisson transformation
\begin{align}
    &y_{itak}^\star \sim \text{xPoisson}(\kappa_{itak}), \\
    &\log(\kappa_{itak}) 
    = \underbrace{\theta_{ita}}_{\text{Observation (IID)}}
    + \underbrace{\beta_k}_{\text{Category (IID)}}
    + \underbrace{\alpha_{ak}}_{\text{Age (IID)}} \\
    &+ \underbrace{\zeta_{ck}}_{\text{Country (IID)}} 
    + \underbrace{\phi_{ik}}_{\text{Spatial (Besag)}} 
    + \underbrace{\gamma_{tk}}_{\text{Temporal (AR1)}}
\end{align}
where $p_{itak} = \text{softmax}(\kappa_{ita})_k$
* To differentiate $3^{+}$ we used the 13 surveys with a transactional sex question to fit a survey-weighted logistic regression
\begin{align}
    &y_{ia4}^\star \sim \text{xBinomial} \left( y_{ia3} + y_{ia4}, p_{ia4} / (p_{ia3} + p_{ia4}) \right), \\
    &\text{logit}(p_{ia4} / (p_{ia3} + p_{ia4}))
    = \beta_0
    + \beta_\texttt{cfswever} x_c \\
    &+ \underbrace{\alpha_a}_{\text{Age (IID)}}
    + \underbrace{\zeta_c}_{\text{Country (IID)}}
    + \underbrace{\phi_i}_{\text{Spatial (Besag)}}
\end{align}
where $x_c$ is the proportion of men in each country who are clients of FSW [@hodgins2021cfsw]
* We aligned our FSW estimates to the national-level UNAIDS Key Populations Atlas [@johnston2022deriving]
* Using the Poisson formulation facilitated inference using integrated nested Laplace approximation [@rue2009approximate] via `R-INLA`
* We estimated incidence and number of new infections by risk group using the risk ratios to disaggregate Naomi model [@eaton2021naomi] general population incidence estimates
